---
title: "BT Exploratory Analysis"
author: "Craig Wells"
date: "March 2, 2021"
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: inline
---

```{r}
#Load the dataset.
BT=read.csv("BT.csv",header=TRUE)
#Recall the column names.
names(BT)
#Generate a boxplot of the Eggs column.
boxplot(BT$Eggs, xlab="Eggs", ylab="Count")
```

There are some outliers, but they should be true values.

```{r}
#Generate a boxplot of the Weight column.
boxplot(BT$WT, xlab="Weight", ylab="Grams")
```

There are some outliers, but they should be true values.

```{r}
#Generate a boxplot of the Total Length column
boxplot(BT$TL, xlab="Total Length", ylab="Millimeters")
```

There are some outliers, but they should be true values.

```{r}
#Generate a boxplot of the Fork Length column
boxplot(BT$FL, xlab="Fork Length", ylab="Millimeters")
```

There are some outliers, but they should be true values.

```{r}
#Generate a historgram of Eggs
BT$Eggs=as.numeric(BT$Eggs)
hist(BT$Eggs,xlab="Eggs",main="Eggs Histogram")
#Generate a QQ Plot and line for eggs.
qqnorm(BT$Eggs)
qqline(BT$Eggs)
```

These data are not normally distributed.

```{r}
#Generate a historgram of Weight
hist(BT$WT,xlab="Weight",main="Weight Histogram")
```

These data are not normally distributed.

```{r}
#Generate a historgram of Total Length
hist(BT$TL,xlab="Total Length",main="Total Length Histogram")
```

These data are not normally distributed.

```{r}
#Generate a historgram of Fork Length
hist(BT$FL,xlab="Fork Length",main="Fork Length Histogram")
```

These data are not normally distributed

```{r}
#Scatterplot of Eggs vs Weight
plot(BT$WT,BT$Eggs,xlab="Weight (g)",ylab="No. eggs")

#Linear regression for Eggs vs WT
mymodel=lm(Eggs~WT,data=BT)
abline(mymodel)
```

The relationship is fairly linear.
Linear Regression seems to fit the points fairly well.

```{r}
#Scatterplot of Eggs vs Total Length
plot(BT$TL,BT$Eggs,xlab="Total Length (mm)",ylab="No. eggs")
#Linear regression for Eggs vs TL
mymodel2=lm(Eggs~TL,data=BT)
abline(mymodel2)
```

Relationship is not really linear.

```{r}
#Scatterplot of Eggs vs Fork Length Length
plot(BT$FL,BT$Eggs,xlab="Total Length (mm)",ylab="No. eggs")
#Linear regression for Eggs vs TL
mymodel3=lm(Eggs~FL,data=BT)
abline(mymodel3)
```

Relationship is not really linear.